---
title: "Topic Modelling Analysis"
subtitle: "BERTopic Analysis of Extremist Telegram Channels — Full Statistical Analysis and Visualisations"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 12, fig.height = 8, dpi = 300)

library(tidyverse)
library(scales)
library(viridis)
library(patchwork)
library(knitr)

BASE_DIR <- "/Volumes/One Touch/terrorgram"
RESULTS_DIR <- file.path(BASE_DIR, "topic_modelling")
FIGURES_DIR <- file.path(BASE_DIR, "figures_tm")
dir.create(FIGURES_DIR, showWarnings = FALSE, recursive = TRUE)

CATEGORY_LABELS <- c(
  "764" = "764",
  "terrorgram" = "Terrorgram",
  "white-supremacist" = "White Supremacist"
)

CATEGORY_COLORS <- c(
  "764" = "#e74c3c",
  "terrorgram" = "#3498db",
  "white-supremacist" = "#2ecc71"
)

theme_publication <- function() {
  theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(face = "bold", size = 12),
      axis.title = element_text(size = 10),
      legend.title = element_text(face = "bold", size = 10),
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      strip.text = element_text(face = "bold")
    )
}
```

## Data Loading

```{r load-data}
labels <- read_csv(file.path(RESULTS_DIR, "step3_validation/topic_labels_with_coherence.csv"))
coherence <- read_csv(file.path(RESULTS_DIR, "step3_validation/topic_coherence.csv"))
diversity <- read_csv(file.path(RESULTS_DIR, "step3_validation/topic_diversity.csv"))
trends <- read_csv(file.path(RESULTS_DIR, "step4_temporal/topic_trends.csv"))
```

The topic modelling pipeline fitted separate BERTopic models for each of the three movement categories, yielding 19 topics per category (plus a noise topic). The data below summarise the model outputs.

---

## Summary Statistics

### Topics per Category

```{r summary-topics}
topic_summary <- labels %>%
  group_by(category) %>%
  summarise(
    n_topics = n(),
    total_messages = sum(message_count),
    mean_messages = round(mean(message_count)),
    median_messages = round(median(message_count)),
    .groups = "drop"
  ) %>%
  mutate(category_label = CATEGORY_LABELS[category])

topic_summary %>%
  select(category_label, n_topics, total_messages, mean_messages, median_messages) %>%
  kable(col.names = c("Category", "Topics", "Total Messages", "Mean Messages", "Median Messages"),
        caption = "Topic model summary by category",
        format.args = list(big.mark = ","))
```

### Coherence Summary

```{r summary-coherence}
coherence_summary <- coherence %>%
  group_by(category) %>%
  summarise(
    n = n(),
    mean_npmi = round(mean(coherence_npmi, na.rm = TRUE), 4),
    sd_npmi = round(sd(coherence_npmi, na.rm = TRUE), 4),
    min_npmi = round(min(coherence_npmi, na.rm = TRUE), 4),
    median_npmi = round(median(coherence_npmi, na.rm = TRUE), 4),
    max_npmi = round(max(coherence_npmi, na.rm = TRUE), 4),
    pct_positive = percent(mean(coherence_npmi > 0, na.rm = TRUE), accuracy = 0.1),
    .groups = "drop"
  ) %>%
  mutate(category_label = CATEGORY_LABELS[category])

coherence_summary %>%
  select(category_label, n, mean_npmi, sd_npmi, min_npmi, median_npmi, max_npmi, pct_positive) %>%
  kable(col.names = c("Category", "N", "Mean", "SD", "Min", "Median", "Max", "% Positive"),
        caption = "NPMI coherence summary by category")
```

### Diversity Summary

Topic vocabulary diversity measures the proportion of unique terms across all topics within each category. Higher diversity indicates that topics use more distinct vocabulary.

```{r summary-diversity}
diversity %>%
  mutate(
    category_label = CATEGORY_LABELS[category],
    diversity = percent(diversity, accuracy = 0.1)
  ) %>%
  select(category_label, diversity) %>%
  kable(col.names = c("Category", "Vocabulary Diversity"),
        caption = "Topic vocabulary diversity (proportion of unique terms across all topics)")
```

764 had the highest topic diversity (`r diversity %>% filter(category == "764") %>% pull(diversity) %>% percent(accuracy = 0.1)`), indicating the most distinct vocabulary across topics. White supremacist channels showed the lowest topic diversity (`r diversity %>% filter(category == "white-supremacist") %>% pull(diversity) %>% percent(accuracy = 0.1)`), and Terrorgram occupied an intermediate position (`r diversity %>% filter(category == "terrorgram") %>% pull(diversity) %>% percent(accuracy = 0.1)`).

---

## Topic Distribution by Category

```{r topic-distribution, fig.width=14, fig.height=10}
p_dist <- labels %>%
  mutate(
    category_label = CATEGORY_LABELS[category],
    label_short = str_trunc(label, 25)
  ) %>%
  ggplot(aes(x = reorder(label_short, message_count), y = message_count, fill = category)) +
  geom_col(alpha = 0.8) +
  coord_flip() +
  facet_wrap(~category_label, scales = "free", ncol = 3) +
  scale_fill_manual(values = CATEGORY_COLORS, guide = "none") +
  scale_y_log10(labels = comma) +
  labs(
    title = "Topic Distribution by Message Volume",
    x = NULL,
    y = "Message Count"
  ) +
  theme_publication() +
  theme(
    axis.text.y = element_text(size = 7),
    strip.text = element_text(size = 10)
  )

p_dist

ggsave(file.path(FIGURES_DIR, "topic_distribution.pdf"), p_dist, width = 14, height = 10)
```

---

## Coherence Comparison

```{r coherence, fig.width=14, fig.height=12}
p_coh_a <- coherence %>%
  mutate(category_label = CATEGORY_LABELS[category]) %>%
  ggplot(aes(x = category_label, y = coherence_npmi, fill = category)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  geom_jitter(width = 0.2, alpha = 0.5, size = 2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  scale_fill_manual(values = CATEGORY_COLORS, guide = "none") +
  labs(
    title = "Topic Coherence by Category",
    x = NULL,
    y = "NPMI Coherence"
  ) +
  theme_publication()

p_coh_b <- coherence %>%
  mutate(
    category_label = CATEGORY_LABELS[category],
    label_short = str_trunc(label, 20),
    color = ifelse(coherence_npmi < 0, "negative", "positive")
  ) %>%
  ggplot(aes(x = reorder(label_short, coherence_npmi), y = coherence_npmi, fill = color)) +
  geom_col(alpha = 0.8) +
  coord_flip() +
  facet_wrap(~category_label, scales = "free_y", ncol = 3) +
  scale_fill_manual(values = c("negative" = "#e74c3c", "positive" = "#2ecc71"), guide = "none") +
  geom_hline(yintercept = 0, linewidth = 0.3) +
  labs(
    title = "Coherence Score by Topic",
    x = NULL,
    y = "NPMI Coherence"
  ) +
  theme_publication() +
  theme(axis.text.y = element_text(size = 9))

p_coherence <- p_coh_a / p_coh_b + plot_layout(heights = c(1, 2))
p_coherence

ggsave(file.path(FIGURES_DIR, "coherence_comparison.pdf"), p_coherence, width = 14, height = 12)
```

---

## Thematic Overlap Venn Diagram

The Venn diagram shows the manually assigned thematic categories for each movement (excluding "Other"), highlighting shared and unique themes across the three movements.

```{r venn, fig.width=8, fig.height=7}
library(ggVennDiagram)

# Theme sets per category (excluding Other)
theme_sets <- list(
  "764" = c("CSAM/Exploitation", "Racism/WN", "Antisemitism",
            "Gaming", "Non-English", "OPSEC/OSINT", "Appearance"),
  "Terrorgram" = c("Accelerationism", "Antisemitism", "Firearms/Weapons",
                    "Fitness", "Gaming", "Non-English",
                    "Occult/Pagan", "Propaganda", "Racism/WN"),
  "White Supremacist" = c("Accelerationism", "Antisemitism", "Appearance",
                           "Firearms/Weapons", "Fitness",
                           "Non-English", "Occult/Pagan", "Racism/WN",
                           "Survivalism")
)

# Build the base Venn with no labels, then extract region positions
p_base <- ggVennDiagram(theme_sets, label = "count", label_alpha = 0, edge_size = 0.5)
built <- ggplot_build(p_base)

# Layer 4 has the region labels; extract their positions
region_coords <- built$data[[4]][, c("x", "y")]

# Get region items in matching order
venn_obj <- Venn(theme_sets)
data <- process_data(venn_obj)
regions <- venn_region(data)

region_coords$label_text <- sapply(regions$item, function(items) {
  if (length(items) == 0) return("")
  paste(items, collapse = "\n")
})

# Rebuild plot with custom text labels instead of counts
p_venn <- ggVennDiagram(theme_sets, label = "none",
                         label_alpha = 0, edge_size = 0.5) +
  geom_text(data = region_coords,
            aes(x = x, y = y, label = label_text),
            size = 2.8, lineheight = 1.15) +
  scale_fill_gradient(low = "white", high = "#3498db", guide = "none") +
  scale_color_manual(values = c("764" = "#e74c3c",
                                "Terrorgram" = "#3498db",
                                "White Supremacist" = "#2ecc71")) +
  labs(
    title = "Thematic Overlap Across Categories",
    subtitle = "Shared and unique theme categories (excluding Other)"
  ) +
  theme_void() +
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    plot.subtitle = element_text(size = 10, hjust = 0.5),
    legend.position = "none"
  )

p_venn

ggsave(file.path(FIGURES_DIR, "venn_diagram.pdf"), p_venn, width = 8, height = 7)
```

---

## Emerging and Declining Topics

```{r trends, fig.width=14, fig.height=8}
p_trends <- trends %>%
  filter(trend != "Stable") %>%
  mutate(
    category_label = CATEGORY_LABELS[category],
    label_short = str_trunc(label, 30),
    change_pct_capped = pmax(pmin(change_pct, 500), -100)
  ) %>%
  ggplot(aes(x = reorder(label_short, change_pct_capped), y = change_pct_capped, fill = trend)) +
  geom_col(alpha = 0.8) +
  coord_flip() +
  facet_wrap(~category_label, scales = "free_y") +
  scale_fill_manual(values = c("Emerging" = "#2ecc71", "Declining" = "#e74c3c")) +
  geom_hline(yintercept = 0, linewidth = 0.3) +
  labs(
    title = "Emerging and Declining Topics",
    subtitle = "Change in prevalence (Pre-2023 vs Post-2023)",
    x = NULL,
    y = "Change (%)",
    fill = "Trend"
  ) +
  theme_publication() +
  theme(axis.text.y = element_text(size = 9))

p_trends

ggsave(file.path(FIGURES_DIR, "topic_trends.pdf"), p_trends, width = 14, height = 8)
```

### Trend Summary

```{r trend-summary}
trend_summary <- trends %>%
  count(category, trend) %>%
  pivot_wider(names_from = trend, values_from = n, values_fill = 0) %>%
  mutate(category_label = CATEGORY_LABELS[category])

trend_summary %>%
  select(category_label, everything(), -category) %>%
  kable(caption = "Number of topics by trend direction per category")
```

```{r trend-top}
trends %>%
  filter(trend != "Stable") %>%
  group_by(category) %>%
  slice_max(abs(change_pct), n = 5) %>%
  ungroup() %>%
  mutate(
    category_label = CATEGORY_LABELS[category],
    change_pct = round(change_pct, 1)
  ) %>%
  select(category_label, label, trend, change_pct) %>%
  kable(col.names = c("Category", "Topic", "Trend", "Change (%)"),
        caption = "Top 5 most changed topics per category (by absolute change)")
```
